% document type and language
\documentclass[12pt]{article}

% standard packages
\usepackage{amsmath, bm, empheq, mathrsfs, natbib, cancel}

% normal margins
\usepackage[margin=1in]{geometry}

% plane blue hyperlinks
\usepackage[colorlinks]{hyperref}
\hypersetup{
	colorlinks = true,
	linkcolor=blue,
	citecolor=blue
}

% common macros
\input{../macros.tex}

% other macros
\newcommand{\vecrot}{\bm{\Omega}}
\newcommand{\vecr}{\bm{r}}
\newcommand{\xpar}{x_\parallel}
\newcommand{\epar}{\e_\parallel}
\newcommand{\upar}{u_\parallel}
\newcommand{\uperp}{\vecu_\perp}
\newcommand{\veci}{\bm{I}}

% date, author, title
\date{\today}
\author{Loren Matilsky}
\title{Induction term in spherical coordinates}

\begin{document}
\maketitle

\section{The problem with the traditional induction terms}
We consider the ideal (resistance-free) magnetohydrodynamic (MHD) induction equation:
\begin{align}
	\five\pderiv{\vecb}{t} &= \curl(\vecu\times\vecb) \label{eq:ind1}\define\veci,\\
	&= \vecb\dotgrad\vecu - \vecu\dotgrad\vecb -(\Div\vecu)\vecb, \label{eq:ind2}
\end{align}
where $\vecb$ and $\vecu$ are the vector magnetic and velocity fields (respectively) and $\veci$ is the vector induction. The three terms on the right-hand-side of Equation \eqref{eq:ind2} are often interpreted as ``shear," ``advection," and ``compression," respectively. However, this interpretation is problematic in general for two reasons:

\begin{enumerate}
	\item The so-called shear and compression terms contain sub-terms that cancel; in particular, only velocity motions \textit{perpendicular} to magnetic-field lines can shear or compress. \label{enum:problem1}
	\item Solid-body rotation (which is a non-shearing motion that simply rotates the whole field configuration) shows up in the so-called shear and advection terms in a strange way. \label{enum:problem2}
\end{enumerate}

Finally, even after these issues have been addressed, resolving the final terms into a particular curvilinear system (e.g., spherical coordinates) seems to present a major headache. Our goal here is to explain fully how these problems emerge and propose a tentative solution for the case of spherical coordinates. 

\section{Perpendicular shear and compression}
To see how Problem \ref{enum:problem1} arises, we decompose the velocity field into components parallel and perpendicular to the local direction of $\vecb$:
\begin{align}
	\vecu &\define \upar\epar + \uperp
\end{align} 
Obviously $\vecb=B\xpar$, where $B=|\vecb|$. We denote the Cartesian distance along $\vecb$ by $\xpar$. We also decompose $\vecu$ into its parallel and perpendicular components:
\begin{align}
	\Div\vecu=\pderiv{\upar}{\xpar}+\nabla_\perp\cdot\uperp
\end{align}
We then calculate
\begin{align}
	\vecb\dotgrad\vecu - (\Div\vecu)\vecb&=B\pderiv{}{\xpar}(\upar\epar + \uperp) -\left(\pderiv{\upar}{\xpar}+\nabla_\perp\cdot\uperp\right)B\epar\nonumber\\
	&= \cancel{B\pderiv{\upar}{\xpar}\epar} + B\pderiv{\uperp}{\xpar} -\cancel{\pderiv{\upar}{\xpar} B\epar} - (\nabla_\perp\cdot\uperp)B\epar\nonumber\\
	&= \vecb\dotgrad\uperp - (\nabla_\perp\cdot\uperp)\vecb.
\end{align}
Thus, only motions perpendicular to the local field line (i.e., $\uperp$) can shear or compress $\vecb$.  

\section{Rigid rotation}
To see how Problem \ref{enum:problem2} arises, we consider a velocity field due to rigid rotation at constant angular velocity $\Omega$ about the $z$-axis in a cylindrical coordinate system:
\begin{subequations}
	\begin{align}
		\vecrot &= \Omega\ez=\text{constant}\\
		\vecu&=\vecrot\times\bm{r} = \Omega\lambda\ep
	\end{align}
\end{subequations}
Here, $\lambda$ is the cylindrical radius, $\phi$ the longitude, and $z$ the axial coordinate. In general,  $\e_{(\cdots)}$ denotes a unit vector in the direction of its subscript. We calculate:
\begin{align}
	\Div\vecu&=\Div(\vecrot\times\bm{r})\nonumber\\
	&= \vecrot\dotgrad\times\vecr-\vecr\dotgrad\times\vecrot\nonumber\\
	&= 0\five\text{no compression for rigid rotation (obviously).}
\end{align}
Then:
\begin{align}
	\vecb\dotgrad\vecu&=(\vecb\dotgrad)(\vecrot\times\vecr)\nonumber\nonumber\\
	&= \vecrot\times[(\vecb\dotgrad)(\vecr)]\\
	&= \vecrot\times\vecb\five\text{``shear" for rigid rotation}.
\end{align}
Finally:
\begin{align*}
	-\vecu\dotgrad\vecb &= -\Omega\lambda\ep\dotgrad\vecb\\
	&=-\Omega\pderiv{}{\phi}(B_\lambda\el+B_\phi\ep+B_z\ez)\\
	&=-\Omega\sum_\alpha\left(\pderiv{B_\alpha}{\phi}\right)\e_\alpha-\Omega\sum_\alpha B_\alpha\pderiv{\e_\alpha}{\phi},
\end{align*}
where the index $\alpha$ runs over the three cylindrical coordinates. Note that in the cylindrical coordinate system (or indeed any coordinate system with an axis of rotational symmetry), $\pderivline{\e_\alpha}{\phi}=\e_z\times\e_\alpha$ for each $\alpha$. Thus,
\begin{align*}
	-\Omega\sum_\alpha B_\alpha\pderiv{\e_\alpha}{\phi} &= -\Omega\sum_\alpha B_\alpha\ez\times\e_\alpha\\
	&=-\Omega\ez\times\sum_\alpha B_\alpha\e_\alpha\\
	&=-\vecrot\times\vecb
\end{align*}
and so
\begin{align}
	-\vecu\dotgrad\vecb &= -\Omega\sum_\alpha\left(\pderiv{B_\alpha}{\phi}\right)\e_\alpha-\vecrot\times\vecb \five \text{``advection" for rigid rotation}.
\end{align}
Mathematically, in any coordinate system with a $z$-axis of rotational symmetry, the action of rigid rotation is as follows:
\begin{subequations}
\begin{align}
	\pderiv{\vecb}{t}&=\curl[(\vecrot\times\vecr)\times\vecb]\nonumber\\
	&= \sum_\alpha\left(-\Omega\pderiv{B_\alpha}{\phi}\right)\e_\alpha \label{eq:rottransport1}\\
	\orr \left(\pderiv{}{t}+\Omega\pderiv{}{\phi}\right)B_\alpha&=0\five\text{for each $\alpha$}.\label{eq:rottransport2}
\end{align}
\end{subequations}
If you think about it, this makes sense: All the rigid rotation does is rotate the whole field configuration around the $z$-axis at the rate $\Omega$. If you decide to also rotate at $\Omega$ (so your personal Eulerian time derivative is $\pderivline{}{t}+\Omega\pderivline{}{\phi}$), then each component of the magnetic-field configuration should remain the same in your frame. Note that rotation does \textit{not} advect the vector magnetic field (like the term $-\vecu\dotgrad\vecb$ viewed on its own would suggest), but rather advects the field \textit{components} (as if they were scalars) in any coordinate system with an axis of rotational symmetry. 

\section{Solution for spherical coordinates}
Resolving these issues fully for the spherical coordinate system seems complicated and I am not fully sure how to do it! In particular (for ``full" resolution) we should, separately at each point ($r$,$\theta$,$\phi$):
\begin{enumerate}
	\item Form a local Cartesian coordinate system, say ($x_1$, $x_2$, $x_3$), whose origin lies at the point $(r,\theta,\phi)$. At the origin, ($\e_1$, $\e_2$, $\e_3$) will coincide with ($\er$, $\et$, $\ep$). But slightly away from the origin, ($\e_1$, $\e_2$, $\e_3$) will stay fixed while ($\er$, $\et$, $\ep$) curve away. 
	\item Calculate the velocity-gradient tensor: $\pderivline{u_1}{x_1},\pderivline{u_2}{x_1}, \pderivline{u_3}{x_1}$, etc. While calculating derivatives, be careful to differentiate along the Cartesian coordinates, \textit{not} the curvilinear ones or along the actual $\vecb$-line). Express the final tensor components in spherical coordinates.
	\item Rotate ``into $\vecb$" to form a new primed coordinate system (such that $\e_1^\prime$ points along $\vecb$), calculate the $\pderivline{u_j^\prime}{x_i^\prime}$, and thus form $\pderivline{\upar}{\xpar}$ and $\pderivline{\uperp}{\xpar}$ (note that $\nabla_\perp\cdot\uperp=\Div\vecu- \pderivline{\upar}{\xpar}$). Note that the direction cosines $\e_1^\prime$ makes with ($\e_1$, $\e_2$, $\e_3$) are simply $\br/|\vecb|, \bt/|\vecb|, \bp/|\vecb|$, respectively. Note that both unit vectors and vector components transform like $x_1^\prime=\sum_{j=1}^3R_{1j}x_j$, where $R_{1j}$ is the $j^{th}$ direction cosine.  
	\item Subtract the part of $\uperp$ corresponding to solid-body rotation and put it in the form of Equation \eqref{eq:rottransport1}. 
	\item Exult, because I haven't been able to do this!
\end{enumerate}
Instead of addressing the full problem as just described, I have brute-forced my way into a quasi-solution, canceling obvious terms and expressing what seem to be ``perpendicular shear with no solid-body rotation," ``perpendicular compression," and advection. 

We write:
\begin{align*}
	I_r =\ &\cancel{\br\pderiv{\ur}{r}}   +   \frac{\bt}{r}\pderiv{\ur}{\theta}   +   \frac{\bp}{\rsint}\pderiv{\ur}{\phi}   -   \bcancel{    \frac{\bt\ut+\bp\up}{r}   }\\
	&-\left[   \ur\pderiv{\br}{r}   +   \frac{\ut}{r}\pderiv{\br}{\theta}   +   \frac{\up}{\rsint}\pderiv{\br}{\phi}   -   \bcancel{    \frac{\ut\bt+\up\bp}{r}   }   \right]\\
	&- B_r\left[   \cancel{\pderiv{\ur}{r}}   +    \pderiv{2\ur}{r}   +   \frac{1}{r}\left(  \pderiv{\ut}{\theta}  + \cot\theta\ut  \right)   +   \orsint\pderiv{\up}{\phi}   \right]
\end{align*}
\end{document}